Discovery of s-process enhanced stars in the LAMOST survey

### 2018-02-23 article/ms.tex
final draft

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table \ref{table:table1} including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.

@@

\begin{table*}
\centering
\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

@@

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\section*{Acknowledgements}
We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), Hans-Walter Rix (MPIA) and especially Andrew Casey (Monash) for useful discussions. 
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A. Y. Q. H. was supported by the GROWTH project funded by the National Science Foundation under PIRE Grant No 1545949, and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences. 
This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.

>>>>

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.

@@

%\begin{table*}
%\centering
%\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
%\label{table:table1}
%\begin{adjustbox}{width=1\textwidth}
%\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
%\toprule
%2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
%& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
%J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
%J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
%J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
%J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
%J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
%J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
%J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
%J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
%J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
%\end{tabular}
%\end{adjustbox}
%\end{table*}

@@

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\section*{Acknowledgements}
We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A. Y. Q. H. was supported by the GROWTH project funded by the National Science Foundation under PIRE Grant No 1545949, and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences. 
This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
